\thetitle

### 2020-12-04 sun_phases/spin_qudit_tomo.tex
some changes from review/feedback

% todo: define spherical harmonics

We begin by introducing a set of qudit operators that are analogous to the spherical harmonic functions $Y_{\ell m}$, and which play a central role in our work.
Consider a $d$-state spin qudit with total spin $s\equiv\frac{d-1}{2}$.
The defining property of a spin qudit, distinguishing it from other qudits, is that it describes an angular momentum degree of freedom, which has specific implications for how a spin qudit should transform under the group SO(3) of rotations in 3D space.
Due to the central importance of these transformation rules for a spin qudit, we seek a basis of operators that transform nicely under 3D rotations \footnote{Technically speaking, we seek a basis of operators that transform as an irreducible representation of SO(3).}.
One such basis is that of the {\it polarization operators} \cite{kryszewski2006positivity, bertlmann2008bloch}, defined by
\begin{align}
  T_{\ell m} \equiv \sqrt{\f{2\ell+1}{2s+1}} \sum_{\mu,\nu=-s}^s
  \bk{s\mu;\ell m|s\nu} \op{\nu}{\mu},
  \label{eq:trans_op}
\end{align}
where $\bk{s\mu;\ell m|s\nu}$ is a Clebsh-Gordan coefficient that enforces $\ell\in\set{0,1,\cdots,d-1}$ and $m\in\set{-\ell,-\ell+1,\cdots,\ell}$, such that there are $d^2$ polarization operators in total.
For brevity, we will generally treat the value of $d$ (or $s$) as constant but arbitrary throughout this work, and suppress any explicit dependence of quantities or operators such as $T_{\ell m}$ on $d$.
The polarization operators are orthonormal with respect to the trace inner product, and transform nicely under conjugation:
\begin{align}
  \obk{T_{\ell m }|T_{\ell'm'}}
  = \delta_{\ell\ell'} \delta_{mm'},
  &&
  T_{\ell m}^\dag = \p{-1}^m T_{\ell,-m},
\end{align}
where for any $d\times d$ matrix $X=\sum_{\mu,\nu} X_{\mu\nu} \op{\mu}{\nu}$ we define the $d^2$-component vector $\oket{X} \equiv \sum_{\mu,\nu} X_{\mu\nu} \ket{\mu\nu}$; $\obra{X}$ is the conjugate transpose of $\oket{X}$, such that $\obk{X|Y}=\tr\p{X^\dag Y}$; and $\delta_{kk'}\equiv 1$ if $k=k'$ and $0$ otherwise.
These properties of the polarization operators allow us to expand any density operator $\rho$ in the polarization operator basis as
\begin{align}
  \rho = \sum_{\ell=0}^{d-1} \sum_{m=-\ell}^\ell
  \rho_{\ell m} T_{\ell m},
  &&
  \rho_{\ell m} \equiv \bk{T_{\ell m}^\dag}_\rho,
  \label{eq:trans_state}
\end{align}
where $\bk{X}_\rho\equiv\tr\p{\rho X}=\obk{\rho|X}$, and $\rho^\dag=\rho$ implies that $\rho_{\ell m}^*=\p{-1}^m\rho_{\ell,-m}$.
The polarization operators can be interpreted in terms of an absorption process, whereby $T_{\ell m}\ket\psi$ is (up to normalization) the state obtained after a spin-$s$ state $\ket\psi$ absorbs a particle with total spin $\ell$ and spin projection $m$ onto a fixed quantization axis.
In analogy with the spherical harmonics $Y_{\ell m}$, we will refer to the index $\ell$ as the {\it degree} and $m$ as the {\it order} of $T_{\ell m}$.

The polarization operators are spherical tensor operators, whose degree is preserved under 3D rotations generated by the spin operators $S_\x,S_\y,S_\z$.
Moreover, the degree-$\ell$ polarization operators $T_{\ell m}$ transform identically to spin-$\ell$ particles under 3D rotations (see Appendix \ref{sec:rotations}).
For any triplet of Euler angles $\v\omega=\p{\alpha,\beta,\gamma}$, we can therefore define the rotation operator
\begin{align}
  R\p{\v\omega} \equiv e^{-\i\alpha S_\z} e^{-\i\beta S_\y} e^{-\i\gamma S_\z},
\end{align}
and expand polarization operators in a rotated frame as
\begin{align}
  T_{\v\omega\ell m} \equiv
  R\p{\v\omega}^\dag T_{\ell m} R\p{\v\omega}
  = \sum_{n=-\ell}^\ell D_{nm}^\ell\p{\v\omega} T_{\ell n},
  \label{eq:trans_rot}
\end{align}
where
\begin{align}
  D_{mn}^\ell\p{\v\omega} \equiv \bk{\ell m|R\p{\v\omega}|\ell n}
\end{align}
are (Wigner) rotation matrix elements.
Throughout this work, we will primarily consider rotations of the sphere that take the north pole to a point $\v v=\p{\alpha,\beta}$ at azimuthal angle $\alpha$ and polar angle $\beta$.
For ease of notation, we will therefore implicitly associate Euler angle doublets $\v v=\p{\alpha,\beta}$ with the triplet $\p{\alpha,\beta,0}$, such that $R\p{\v v} \equiv R\p{\alpha,\beta,0}$, $D^\ell_{mn}\p{\v v} \equiv D^\ell_{mn}\p{\alpha,\beta,0}$, and $T_{\v v\ell m} \equiv T_{\p{\alpha,\beta,0},\ell m}$.

As a final point, we mention that the polarization operators $T_{\ell m}$ share a connection to the spherical harmonics $Y_{\ell m}$ that goes beyond the rules for their transformation under 3D rotations.
In fact, the phase-space (Wigner function) representation of $T_{\ell m}$ is proportional to $Y_{\ell m}$.
The phase-space representation of a spin qudit operator $X$ assigns, to each point $\v v$ on the sphere, the number
\begin{align}
  X^{\t{PS}}\p{\v v} \equiv \bk{s_{\v v}|X|s_{\v v}},
\end{align}
where $\ket{s_{\v v}}\equiv R\p{\v v}\ket{s}$ is the state of a spin qudit polarized along $\v v$.
This representation is faithful in the sense that $X$ is uniquely determined by the phase-space values $X^{\t{PS}}\p{\v v}$ at all points $\v v$ on the sphere.
The transformation rules for polarization operators in Eq.~\eqref{eq:trans_rot}, together with the fact that $\bk{s|T_{\ell m}|s}=0$ unless $m=0$, suffice to show that (see Appendix \ref{sec:rotations})
\begin{align}
  T_{\ell m}^{\t{PS}}\p{\v v} = c_\ell Y_{\ell m}\p{\v v},
\end{align}
where the scalar $c_\ell$ simply enforces that $\obk{T_{\ell m}|T_{\ell m}}=1$.
The polarization operators $T_{\ell m}$ are thus a quantum analogue of spherical harmonics $Y_{\ell m}$, which play an important role in phase-space formalisms for spin qudits \cite{li2013weylwignermoyal}.

% todo: add reference for Wigner function, clarify / use different language; mention Husimi distribution

% todo: comment further on this representation, motivating signal recovery via the phase-space representation of qudit states

@@

In order to reconstruct an arbitrary density operator $\rho$ from the expectation values $\bk{T_{\v v\ell,0}}_\rho$, we essentially need to to find a set of coefficients $C_{\ell mk}\p{\v v}$ that would allow us to recover any matrix element $\rho_{\ell m}$ of $\rho$ through
\begin{align}
  \rho_{\ell m}^* = \bk{T_{\ell m}}_\rho
  = \sum_{\v v,k} C_{\ell mk}\p{\v v} \bk{T_{\v vk,0}}_\rho.
  \label{eq:state_recon}
\end{align}
Expanding the rotated polarization operators $T_{\v vk,0}$ into a sum of un-rotated polarization operators, according to Eq.~\eqref{eq:trans_rot}, we find that the recovery condition in Eq.~\eqref{eq:state_recon} is satisfied when
\begin{align}
  T_{\ell m}
  = \sum_{\v v,k,n} C_{\ell mk}\p{\v v}
  D^k_{n,0}\p{\v v} T_{kn}.
\end{align}
Orthogonality of the polarization operators motivates the ansatz $C_{\ell mk}\p{\v v}=\delta_{k\ell}C_{\ell m}\p{\v v}$, which in turn implies that
\begin{align}
  \sum_{\v v} C_{\ell m}\p{\v v} D^\ell_{n,0}\p{\v v} = \delta_{mn}
  \label{eq:tomo_recovery}
\end{align}
for all $\ell$.

In fact, the problem of finding suitable axes $V$ and coefficients $C_{\ell m}\p{\v v}$ to satisfy Eq.~\eqref{eq:tomo_recovery} can be mapped onto the well-studied problem of signal recovery on the sphere \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality}.
The signal recovery problem can be stated as follows: given a square-integrable function $f$ on the sphere, with the spherical harmonic expansion
\begin{align}
  f\p{\v v} = \sum_{\ell,m} f_{\ell m} Y_{\ell m}\p{\v v},
\end{align}
where $f_{\ell m}$ are complex coefficients, find a set of points $V=\set{\v v}$ and associated coefficients $\tilde C_{\ell m}\p{\v v}$ with which we can reconstruct $f$, or equivalently its coefficients $f_{\ell m}$, from knowledge of the function's value $f\p{\v v}$ at all points $\v v\in V$; that is
\begin{align}
  f_{\ell m} = \sum_{\v v} \tilde C_{\ell m}\p{\v v} f\p{\v v}
  = \sum_{\v v,k,n} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v} f_{kn}.
\end{align}
Reconstruction of functions with arbitrary coefficients $f_{\ell m}$ implies that
\begin{align}
  \sum_{\v v} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v}
  = \delta_{k\ell} \delta_{mn},
  \label{eq:full_recovery}
\end{align}
which is a stronger version of the condition that we found for the spin qudit tomography problem in Eq.~\eqref{eq:tomo_recovery}.
We will refer to Eq.~\eqref{eq:full_recovery} as the {\it full recovery problem}, and Eq.~\eqref{eq:tomo_recovery} as the the {\it reduced recovery problem}.
Due to the fact that $D^k_{n,0}\p{\v v} = \sqrt{\frac{4\pi}{2\ell+1}}\, Y_{kn}\p{\v v}^*$, any solution to the full recovery problem automatically solves the reduced recovery problem by setting $C_{\ell m}\p{\v v} = \sqrt{\frac{2\ell+1}{4\pi}}\, \tilde C_{\ell m}\p{\v v}^*$.
In principle, this mapping allows us to import a host of existing signal recovery algorithms \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality} for the task of spin qudit tomography.
In practice, spin qudits typically have only a modest dimension $d$, which allows for simpler and optimized tomography protocols that are practical despite worse scaling with $d$ (see Section \ref{sec:protocol}).

@@

Since
\begin{enumerate*}
\item there are at most $2d-1$ polarization operators of any given degree, and
\item measuring spin projection along any single axis provides measurement data for polarization operators of all degrees,
\end{enumerate*}
one might expect that $2d-1$ suitably chosen measurement axes would always suffice to perform full tomography of a $d$-level spin qudit.
In the language of classical signal recovery, we would expect there to exist a set of $2\ell_{\t{max}}+1$ points on the sphere that enable the recovery of any function with fixed degree $\ell\le\ell_{\t{max}}$, given prior knowledge of $\ell$ \footnote{We could further conjecture that if {\it any} set of points $V\subset\Omega_2$ enables the recovery of degree-$\ell_{\t{max}}$ functions on the sphere, then $V$ enables the recovery degree-$\ell$ functions with $\ell\le\ell_{\t{max}}$.
  However, this condition is stronger than necessary to guarantee full recovery of a $d$-level spin qudit state with $2d-1$ measurement axes, which only requires the existence of {\it some} such set of points.}.
Unfortunately, we have no general proof of this conjecture, which requires a deeper analysis of fixed-degree signal recovery on the sphere.
Nonetheless, in the following sections we numerically verify that $2d-1$ points suffice for all $d\le200$.

@@

@@

\begin{figure}[hb]
  \centering
  \includegraphics{qudit_axes.pdf}
  \caption{Empirical measurement-adjusted error scales $\tilde\beta(p)$ with $p$ excess measurement axes, determined by minimizing over $10^3$ choices of measurement axes $V$ or 5 minutes of runtime (for each $p$), whichever comes first.
    Color indicates the qudit dimension $d$.
    The rapid initial drop in $\tilde\beta(p)$ implies that using more measurement axes can substantially lower the upper bound on reconstruction error provided in Eq.~\eqref{eq:bound}, and that these benefits plateau after $p\approx d$.}
  \label{fig:axes}
\end{figure}

@@

Implicitly associating the Euler angle doublet $\v v = \p{\alpha,\beta}$ with the triplet $\p{\alpha,\beta,0}$, the transformation rules in Eq.~\eqref{eq:trans_rot_apndx} imply that we can expand the phase-space representation of $T_{\ell m}$ as
\begin{align}
  T_{\ell m}^{\t{PS}}\p{\v v}
  \equiv \bk{s_{\v v} | T_{\ell m} | s_{\v v}}
  = \bk{s | R\p{\v v}^\dag T_{\ell m} R\p{\v v} | s}
  = D^\ell_{0,m}\p{\v v} \bk{s | T_{\ell,0} | s},
\end{align}
where
\begin{align}
  \bk{s | T_{\ell,0} | s}
  = \sqrt{\f{2\ell+1}{2s+1}} \, \bk{ss;\ell,0|ss}
  = \sqrt{\f{2\ell+1}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}}
    \p{\f{\p{2s}!}{\p{2s-\ell}!}}},
\end{align}
and the properties of the rotation matrix elements $D^\ell_{mn}$ imply that
\begin{align}
  D^\ell_{0,m}\p{\v v} = \sqrt{\f{4\pi}{2\ell+1}} \, Y_{\ell m}\p{\v v},
\end{align}
so
\begin{align}
  T_{\ell m}^{\t{PS}}\p{\v v}
  = \sqrt{\f{4\pi}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}} \p{\f{\p{2s}!}{\p{2s-\ell}!}}} \,
  Y_{\ell m}\p{\v v}.
\end{align}
In this way, the polarization operators are a quantum analogue of spherical harmonics.

>>>>

We begin by introducing a set of qudit operators that are a quantum analogue of the spherical harmonics (in a sense that will be clarified below), and which play a central role in our work.
Consider a $d$-state spin qudit with total spin $s\equiv\frac{d-1}{2}$.
The defining property of a spin qudit, distinguishing it from other qudits, is that it describes an angular momentum degree of freedom, which has specific implications for how a spin qudit should transform under the group SO(3) of rotations in 3D space.
Due to the central importance of these transformation rules for a spin qudit, we seek a basis of operators that transform nicely under 3D rotations \footnote{Technically speaking, we seek a basis of operators that transform as an irreducible representation of SO(3).}.
One such basis is that of the {\it polarization operators} \cite{kryszewski2006positivity, bertlmann2008bloch}, defined by
\begin{align}
  T_{\ell m} \equiv \sqrt{\f{2\ell+1}{2s+1}} \sum_{\mu,\nu=-s}^s
  \bk{s\mu;\ell m|s\nu} \op{\nu}{\mu},
  \label{eq:trans_op}
\end{align}
where $\bk{s\mu;\ell m|s\nu}$ is a Clebsh-Gordan coefficient that enforces $\ell\in\set{0,1,\cdots,d-1}$ and $m\in\set{-\ell,-\ell+1,\cdots,\ell}$, such that there are $d^2$ polarization operators in total.
For brevity, we will generally treat the value of $d$ as constant but arbitrary throughout this work, and we will suppress any explicit dependence of quantities or operators such as $T_{\ell m}$ on $d$.
The polarization operators are orthonormal with respect to the trace inner product, and transform nicely under conjugation:
\begin{align}
  \obk{T_{\ell m }|T_{\ell'm'}}
  = \delta_{\ell\ell'} \delta_{mm'},
  &&
  T_{\ell m}^\dag = \p{-1}^m T_{\ell,-m},
\end{align}
where for any $d\times d$ matrix $X=\sum_{\mu,\nu} X_{\mu\nu} \op{\mu}{\nu}$ we define the $d^2$-component vector $\oket{X} \equiv \sum_{\mu,\nu} X_{\mu\nu} \ket{\mu\nu}$; $\obra{X}$ is the conjugate transpose of $\oket{X}$, such that $\obk{X|Y}=\tr\p{X^\dag Y}$; and $\delta_{kk'}\equiv 1$ if $k=k'$ and $0$ otherwise.
These properties of the polarization operators allow us to expand any density operator $\rho$ in the polarization operator basis as
\begin{align}
  \rho = \sum_{\ell=0}^{d-1} \sum_{m=-\ell}^\ell
  \rho_{\ell m} T_{\ell m},
  &&
  \rho_{\ell m} \equiv \bk{T_{\ell m}^\dag}_\rho,
  \label{eq:trans_state}
\end{align}
where $\bk{X}_\rho\equiv\tr\p{\rho X}=\obk{\rho|X}$, and $\rho^\dag=\rho$ implies that $\rho_{\ell m}^*=\p{-1}^m\rho_{\ell,-m}$.
The polarization operators can be interpreted in terms of an absorption process, whereby $T_{\ell m}\ket\psi$ is (up to normalization) the state obtained after a spin-$s$ state $\ket\psi$ absorbs a particle with total spin $\ell$ and spin projection $m$ onto a fixed quantization axis.
In analogy with the complex spherical harmonics $Y_{\ell m}$, we will refer to $\ell$ as the {\it degree} and $m$ as the {\it order} of $T_{\ell m}$.

The polarization operators are spherical tensor operators, whose degree is preserved under 3D rotations generated by the spin operators $S_\x,S_\y,S_\z$.
Moreover, the degree-$\ell$ polarization operators $T_{\ell m}$ transform identically to spin-$\ell$ particles and spherical harmonics $Y_{\ell m}$ under 3D rotations (see Appendix \ref{sec:rotations}).
For any triplet of Euler angles $\v\omega=\p{\alpha,\beta,\gamma}$, we can therefore define the rotation operator
\begin{align}
  R\p{\v\omega} \equiv e^{-\i\alpha S_\z} e^{-\i\beta S_\y} e^{-\i\gamma S_\z},
\end{align}
and expand polarization operators in a rotated frame as
\begin{align}
  T_{\v\omega\ell m} \equiv
  R\p{\v\omega}^\dag T_{\ell m} R\p{\v\omega}
  = \sum_{n=-\ell}^\ell D_{nm}^\ell\p{\v\omega} T_{\ell n},
  \label{eq:trans_rot}
\end{align}
where
\begin{align}
  D_{mn}^\ell\p{\v\omega} \equiv \bk{\ell m|R\p{\v\omega}|\ell n}
\end{align}
are (Wigner) rotation matrix elements.
Throughout this work, we will primarily consider rotations of the sphere that take the north pole to a point $\v v=\p{\alpha,\beta}$ at azimuthal angle $\alpha$ and polar angle $\beta$.
For ease of notation, we will therefore implicitly associate Euler angle doublets $\v v=\p{\alpha,\beta}$ with the triplet $\p{\alpha,\beta,0}$, such that $R\p{\v v} \equiv R\p{\alpha,\beta,0}$, $D^\ell_{mn}\p{\v v} \equiv D^\ell_{mn}\p{\alpha,\beta,0}$, and $T_{\v v\ell m} \equiv T_{\p{\alpha,\beta,0},\ell m}$.

The polarization operators $T_{\ell m}$ share a connection to the spherical harmonics $Y_{\ell m}$ that goes beyond their indexing and the rules for their transformation under 3D rotations.
In fact, the phase-space representation of $T_{\ell m}$ is proportional to $Y_{\ell m}$.
The phase-space representation of a spin qudit operator $X$ assigns, to each point $\v v$ on the sphere, the complex number
\begin{align}
  X^{\t{PS}}\p{\v v} \equiv \bk{s_{\v v}|X|s_{\v v}},
\end{align}
where $\ket{s_{\v v}}\equiv R\p{\v v}\ket{s}$ is the state of a spin qudit polarized along $\v v$.
This representation is faithful in the sense that $X$ is uniquely determined by the phase-space values $X^{\t{PS}}\p{\v v}$ at all points $\v v$ on the sphere.
The transformation rules for polarization operators in Eq.~\eqref{eq:trans_rot}, together with the fact that $\bk{s|T_{\ell m}|s}=0$ unless $m=0$, suffice to show that (see Appendix \ref{sec:rotations})
\begin{align}
  T_{\ell m}^{\t{PS}}\p{\v v} = c_\ell Y_{\ell m}\p{\v v},
\end{align}
where the scalar $c_\ell$ simply enforces $\obk{T_{\ell m}|T_{\ell m}}=1$.
The polarization operators $T_{\ell m}$ are thus a quantum analogue of the spherical harmonics $Y_{\ell m}$, and play an important role in phase-space formalisms for spin qudits \cite{li2013weylwignermoyal}.

As a special case, the phase-space representation $\rho^{\t{PS}}$ of a qudit state $\rho$ is common known as its Husimi distribution.
Performing tomography on an unknown qudit state $\rho$ is therefore equivalent to reconstructing the unknown distribution $\rho^{\t{PS}}$ on the sphere.
In principle, the representation $\rho^{\t{PS}}$ of a finite-dimensional qudit state $\rho$ can be reconstructed from the values $\rho^{\t{PS}}\p{\v v}=\bk{s_{\v v}|\rho|s_{\v v}}$ at a finite number of points $\v v$ on the sphere.
In practice, the value $\bk{s_{\v v}|\rho|s_{\v v}}$ is determined by measuring spin projection along $\v v$, which also provides measurement data on all spin projections $\bk{\mu_{\v v}|\rho|\mu_{\v v}}$ with $\mu\in\set{s,s-1,\cdots,-s}$ and $\ket{\mu_{\v v}}\equiv R\p{\v v}\ket{\mu}$; one would like to make use of this additional data as well.
We clarify the connection between the quantum problem of reconstructing $\rho$ from spin projection measurements and the classical problem of reconstructing $\rho^{\t{PS}}$ from its values $\rho^{\t{PS}}\p{\v v}$ in the following section.
In addition to providing a new perspective on the problem of spin qudit tomography, the connection will allow us to place upper bounds on the minimal number of measurement axes $\v v$ necessary for full recovery of an unknown state.

@@

In order to reconstruct an arbitrary density operator $\rho$ from the expectation values $\bk{T_{\v v\ell,0}}_\rho$, we essentially need to to find a set of coefficients $C_{\ell mk}\p{\v v}$ that would allow us to recover any matrix element $\rho_{\ell m}$ of $\rho$ through
\begin{align}
  \rho_{\ell m}^* = \bk{T_{\ell m}}_\rho
  = \sum_{\v v,k} C_{\ell mk}\p{\v v} \bk{T_{\v vk,0}}_\rho.
  \label{eq:state_recon}
\end{align}
Expanding the rotated polarization operators $T_{\v vk,0}$ into a sum of un-rotated polarization operators, according to Eq.~\eqref{eq:trans_rot}, we find that the recovery condition in Eq.~\eqref{eq:state_recon} is satisfied when
\begin{align}
  T_{\ell m}
  = \sum_{\v v,k,n} C_{\ell mk}\p{\v v} D^k_{n,0}\p{\v v} T_{kn}.
\end{align}
Orthogonality of the polarization operators then implies the decomposition $C_{\ell mk}\p{\v v}=\delta_{\ell k}C_{\ell m}\p{\v v}$, and in turn
\begin{align}
  \sum_{\v v} C_{\ell m}\p{\v v} D^\ell_{n,0}\p{\v v}
  = \delta_{mn}
  \label{eq:tomo_recovery}
\end{align}
for all $\ell$.
In fact, the problem of finding suitable axes $V$ and coefficients $C_{\ell m}\p{\v v}$ to satisfy Eq.~\eqref{eq:tomo_recovery} can be mapped onto the well-studied problem of signal recovery on the sphere \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality}.
The signal recovery problem can be stated as follows: given a square-integrable function $f$ on the sphere, with the spherical harmonic expansion
\begin{align}
  f\p{\v v} = \sum_{\ell,m} f_{\ell m} Y_{\ell m}\p{\v v},
\end{align}
where $f_{\ell m}$ are complex coefficients, find a set of points $V=\set{\v v}$ and associated coefficients $\tilde C_{\ell m}\p{\v v}$ with which we can reconstruct $f$, or equivalently its coefficients $f_{\ell m}$, from knowledge of the function's value $f\p{\v v}$ at all points $\v v\in V$; that is
\begin{align}
  f_{\ell m} = \sum_{\v v} \tilde C_{\ell m}\p{\v v} f\p{\v v}
  = \sum_{\v v,k,n} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v} f_{kn}.
\end{align}
Reconstruction of functions with arbitrary coefficients $f_{\ell m}$ implies that
\begin{align}
  \sum_{\v v} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v}
  = \delta_{\ell k} \delta_{mn},
  \label{eq:full_recovery}
\end{align}
which is a stronger version of the condition that we found for the spin qudit tomography problem in Eq.~\eqref{eq:tomo_recovery}.
We will refer to Eq.~\eqref{eq:full_recovery} as the {\it full recovery problem}, and Eq.~\eqref{eq:tomo_recovery} as the the {\it reduced recovery problem}.
Due to the fact that $D^k_{n,0}\p{\v v} = \sqrt{\frac{4\pi}{2\ell+1}}\, Y_{kn}\p{\v v}^*$, any solution to the full recovery problem automatically solves the reduced recovery problem by setting $C_{\ell m}\p{\v v} = \sqrt{\frac{2\ell+1}{4\pi}}\, \tilde C_{\ell m}\p{\v v}^*$.
In principle, this mapping allows us to import a host of existing signal recovery algorithms \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality} for the task of spin qudit tomography.
In practice, spin qudits typically have only a modest dimension $d$, which allows for simpler and optimized tomography protocols that are practical despite worse scaling with $d$ (see Section \ref{sec:protocol}).

@@

Since
\begin{enumerate*}
\item there are at most $2d-1$ polarization operators of any given degree, and
\item measuring spin projection along a single axis provides measurement data for polarization operators of all degrees,
\end{enumerate*}
one might expect that $2d-1$ suitably chosen measurement axes would always suffice to perform full tomography of a $d$-level spin qudit.
In the language of classical signal recovery, we would expect there to exist a set of $2\ell_{\t{max}}+1$ points on the sphere that enable the recovery of any function with fixed degree $\ell\le\ell_{\t{max}}$, given prior knowledge of $\ell$ \footnote{We could further conjecture that if {\it any} set of points $V$ enables the recovery of degree-$\ell_{\t{max}}$ functions on the sphere, then $V$ enables the recovery degree-$\ell$ functions with $\ell\le\ell_{\t{max}}$.
  However, this condition is stronger than necessary to guarantee full recovery of a $d$-level spin qudit state with $2d-1$ measurement axes, which only requires the existence of {\it some} such set of points.}.
Unfortunately, we have no general proof of this conjecture, which requires a deeper analysis of fixed-degree signal recovery on the sphere.
Nonetheless, in the following section we numerically verify that $2d-1$ points suffice for all $d\le200$.

@@

\begin{figure}
  \centering
  \includegraphics{qudit_axes.pdf}
  \caption{Empirical measurement-adjusted error scales $\tilde\beta(p)$ with $p$ excess measurement axes, determined by minimizing over $10^3$ choices of measurement axes $V$ or 5 minutes of runtime (for each $p$), whichever comes first.
    Color indicates the qudit dimension $d$.
    The rapid initial drop in $\tilde\beta(p)$ implies that using more measurement axes can substantially lower the upper bound on reconstruction error provided in Eq.~\eqref{eq:bound}, and that these benefits plateau after $p\approx d$.}
  \label{fig:axes}
\end{figure}

@@

@@

Implicitly associating the Euler angle doublet $\v v = \p{\alpha,\beta}$ with the triplet $\p{\alpha,\beta,0}$, the transformation rules in Eq.~\eqref{eq:trans_rot_apndx} imply that we can expand the phase-space representation of $T_{\ell m}$ as
\begin{align}
  T_{\ell m}^{\t{PS}}\p{\v v}
  \equiv \bk{s_{\v v} | T_{\ell m} | s_{\v v}}
  = \bk{s | R\p{\v v}^\dag T_{\ell m} R\p{\v v} | s}
  = D^\ell_{0,m}\p{\v v} \bk{s | T_{\ell,0} | s},
\end{align}
where
\begin{align}
  \bk{s | T_{\ell,0} | s}
  = \sqrt{\f{2\ell+1}{2s+1}} \, \bk{ss;\ell,0|ss}
  = \sqrt{\f{2\ell+1}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}}
    \p{\f{\p{2s}!}{\p{2s-\ell}!}}},
\end{align}
and the properties of the rotation matrix elements $D^\ell_{mn}$ imply that
\begin{align}
  D^\ell_{0,m}\p{\v v} = \sqrt{\f{4\pi}{2\ell+1}} \, Y_{\ell m}\p{\v v},
\end{align}
so
\begin{align}
  T_{\ell m}^{\t{PS}}\p{\v v}
  = \sqrt{\f{4\pi}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}} \p{\f{\p{2s}!}{\p{2s-\ell}!}}} \,
  Y_{\ell m}\p{\v v}.
\end{align}
In this way, the polarization operators are a quantum analogue of the spherical harmonics.
